\Large Ten Simple Rules for Scientific Fraud \& Misconduct

### 2017-07-24 article.tex
Typo
Update

\begin{tikzpicture}[remember picture, overlay]
    \node[xshift=-2.85cm,yshift=-2.85cm] at (current page.north east) {
        \includegraphics[width=3cm]{stample}
    };
\end{tikzpicture}

@@

If you are reluctant to manipulate your data, you still have the option of
searching through your results to find anything that reaches significance 
(a.k.a. p-hacking). This can provide an appealing alternative to scientific misconduct. What is the p value of your NHST (Null Hypothesis
Significance Test)? If it's close to your field's standard one of the many qualification
proposed by
\href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
  Hankins} to report your results? Can't you use expression such as {\em nearly
  acceptable level of significance (p=0.06)}, {\em very closely brushed the
  limit of statistical significance (p=0.051)} or {\em weakly statistically
  significant (p=0.0557)}? While these statements don't make much sense, they might
be sufficient to convince a naive reviewer or reader.

If you're
suffering from a bi-polar p-value disorder, however (a term coined by
\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
  Lakens}), you'll want to reach the magical 0.05 threshold. It might be much easier than you think to portray your data as significant! The correct method for calculating the
infamous p-value is barely understood by many students, teachers, and
researchers \citep{haller:2002,lecoutre:2003}. The current situation is so bad that the American Statistical Association had to release a
statement to explain p's correct usage \citep{wasserstein:2016,};
Nature has issued a warning as well
\citep{baker:2016}. Consequently, before hacking your results, it might be wise
to re-read your classics
\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014}. A warning for those of you in psychology: you have to take extra-precaution because this field has drawn attention for the unusual distribution of
p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. There's now software called statcheck that can be used to recalculate the p values in your paper \citep{nuijten:2015,epskamp:2016}, making it difficult to get away with misleading statistics. Although some have called checking the results of others {\em
  methodological terrorism} \citep{finske:2016}, it might be enough to scare some away from the dark side of Science.

@@

Of course, you cannot literally take an excerpt from an
article to insert it in yours. You'd run the risk of creating a situation where the reviewer found his own text in yours. Consequently, if you
really intend to plagiarize, you'll need to transform the text drastically to
avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
detection by dedicated software (e.g. iThenticate). This software is used by
universities and journals for tracking people just like you. As the databases behind these services grow, plagiarism is becoming harder and harder. Even
self-plagiarism is not allowed by a vast majority of scientific journals. All of this means that you have to be really innovative in your plagiarism techniques \citep{long:2009}. We've reached the point where writing your own text might be an easier option.

@@

Even if you avoid all the pitfalls discussed above, you're in the clear yet. Depending on the
journal you target, you may still encounter problems with the review
process. If reviewers are picky, they may ask annoying questions,
request more information or experiments, ask for a major revision and/or reject your submission entirely. Can you imagine how this would make you feel after all your hard work
fabricating the data and plagiarized the article? There's even the risk that they'll notice your malpractice. Fortunately, there is a simple solution: write your
own review!

@@

If you intend to persist in a rogue scientific career, you have to be aware that
you're likely to get caught sooner or later. The number of researcher to have never been caught is probably low; only the best can hope to be caught only after their death
\citep{degroote:2016,}. But being caught while you're still breathing does not mean you career will come to
an end. There is a set of simple rules to follow if you need to deny scientific misconduct:
\begin{itemize}
  \item If you're first author, explain you were supervised by the last author and
    had no choice.
  \item If you're last author, explain you were not aware of the misconduct of
    the first author.
  \item If your name is not first nor last, claim that you didn't even know your
    name appeared in the publication.
  \item If your name appears because of {\em gift authorship}, just admit it.
    It might be considered misconduct, but fraud is much worse.
  \item The intern, who cannot be contacted because he/she left academia, is
    responsible for everything
  \item Send threatening letters to those who have spotted your misconduct
  \item Follow through on those threats and sue'em all
\end{itemize}
If you're lucky enough, one of the above will work and things should be back to
normal. All of this is easier, of course, if you're supported by you employer because you've been
labeled a rising star.

>>>>

\begin{tikzpicture}[remember picture, overlay]
    \node[xshift=-2.85cm,yshift=-2.85cm] at (current page.north east) {
        \includegraphics[width=3cm]{stample.pdf}
    };
\end{tikzpicture}

@@

If you are reluctant to manipulate your data, you still have the option of
searching through your results to find anything that reaches significance 
(a.k.a. p-hacking). This can provide an appealing alternative to scientific misconduct. What is the p value of your NHST (Null Hypothesis
Significance Test)? If it's close to your field's standard, one of the many qualification
proposed by
\href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
  Hankins} might just do the trick. Can't you use expression such as {\em nearly
  acceptable level of significance (p=0.06)}, {\em very closely brushed the
  limit of statistical significance (p=0.051)} or {\em weakly statistically
  significant (p=0.0557)}? While these statements don't make much sense, they might
be sufficient to convince a naive reviewer or reader.

If you're
suffering from a bi-polar p-value disorder (a term coined by
\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
  Lakens}), you'll want to reach the magical 0.05 threshold. It might be much easier than you think to portray your data as significant! The correct method for calculating the
infamous p-value is barely understood by many students, teachers, and
researchers \citep{haller:2002,lecoutre:2003}. The current situation is so bad that the American Statistical Association had to release a
statement to explain p's correct usage \citep{wasserstein:2016};
Nature has issued a warning as well
\citep{baker:2016}. Consequently, before hacking your results, it might be wise
to re-read your classics
\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014}. A warning for those of you in psychology: you have to take extra-precaution because this field has drawn attention for the unusual distribution of
p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. There's now software called statcheck that can be used to recalculate the p values in your paper \citep{nuijten:2015,epskamp:2016}, making it difficult to get away with misleading statistics. Although some have called checking the results of others {\em
  methodological terrorism} \citep{finske:2016}, it might be enough to scare some away from the dark side of Science.

@@

Of course, you cannot literally take an excerpt from an
article to insert it in yours. You'd run the risk of creating a situation where the reviewer found his own text in yours. Consequently, if you
really intend to plagiarize, you'll need to transform the text drastically to
avoid detection by humans \citep{dorigo:2015} and more importantly, to avoid
detection by dedicated software (e.g. iThenticate). This software is used by
universities and journals for tracking people just like you. As the databases behind these services grow, plagiarism is becoming harder and harder. Even
self-plagiarism is not allowed by a vast majority of scientific journals. All of this means that you have to be really innovative in your plagiarism techniques \citep{long:2009}. We've reached the point where writing your own text might be an easier option.

@@

Even if you avoid all the pitfalls discussed above, you're not in the clear yet. Depending on the
journal you target, you may still encounter problems with the review
process. If reviewers are picky, they may ask annoying questions,
request more information or experiments, ask for a major revision and/or reject your submission entirely. Can you imagine how this would make you feel after all your hard work
fabricating the data and plagiarized the article? There's even the risk that they'll notice your malpractice. Fortunately, there is a simple solution: write your
own review!

@@

If you intend to persist in a rogue scientific career, you have to be aware that
you're likely to get caught sooner or later. The number of researcher to have never been caught is probably low; only the best can hope to be caught only after their death
\citep{degroote:2016}. But being caught while you're still breathing does not mean you career will come to
an end. There is a set of simple rules to follow if you need to deny scientific misconduct:
\begin{itemize}
  \item If you're first author, explain you were supervised by the last author and
    had no choice.
  \item If you're last author, explain you were not aware of the misconduct of
    the first author.
  \item If your name is not first nor last, claim that you didn't even know your
    name appeared in the publication.
  \item If your name appears because of {\em gift authorship}, just admit it.
    It might be considered misconduct, but fraud is much worse.
  \item The intern, who cannot be contacted because he/she left academia, is
    responsible for everything
  \item Send threatening letters to those who have spotted your misconduct
  \item Follow through on those threats and sue'em all
\end{itemize}
If you're lucky enough, one of the above will work and things should be back to
normal. All of this is easier, of course, if you're supported by you employer because you've been
labeled a rising star.
